Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-05-08 krs-survey.tex
Added section on self knowledge

>>>>

\subsubsection{Self-Knowledge}

``Self-knowledge'' is the term used in psychology to describe the knowledge
that an individual has, acquires or infers about itself through its
experiences. It answers the question ``What am I like?''.

For a robot to have at its disposal self-knowledge is closely link to the
introspective capability that we have previously mentioned
(section~\ref{sect|introspection})

\subsubsection{Alignment with Standard Upper-Ontologies}
